---
title: "castro_analysis"
output: pdf_document
date: "2026-01-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(tidyr)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
```

### Load the JSONL data into R

Step by step:

- `file("castro_FINAL.jsonl", "r")`
  - Opens the JSONL file in **read mode**
  - Stores the open connection in `con`

- `stream_in(con)`
  - Reads the JSONL file **line by line**
  - Converts each JSON object into a row of a data frame

- `df <- ...`
  - Stores the result as a table-like `df`

```{r}
con <- file("castro_FINAL.jsonl","r")
df.castro <- tibble(stream_in(con))

df.castro <- df.castro %>% 
  mutate(messy = str_detect(response, "_"),
         clean_response = ifelse(str_detect(response, "_"), "", response))

summary(df.castro)

df.download <- df.castro %>% 
  select(messy,response,clean_response,response_site, participants,date, collect_time, slow,order,pair_id) %>% 
  arrange(desc(messy))

write_csv(df.download, "the_castro_needs_cleaning.csv")

```

```{r read csv}

df.castro <- tibble(read_csv("clean_final_responses.csv")) %>% 
  filter(response_site == "castro")

df.castro

```


```{r}
plot <- df %>% filter(response_site == 'marina') %>% 
  select(fieldsite, participants, fieldworker, response_site, response_gay, response_euphemism, response_diversity, order) %>% 
  mutate(response_gay_and_euphemism = response_gay + response_euphemism)%>% 
  ggplot(aes(x=fieldsite,y=response_diversity))+
           stat_summary(fun = "mean",
                        geom = "bar") +
  labs(
    title = "Proportion responses describing Marina with diversity",
    x = "Fieldsite",
    y = "Proportion diversity responses / total",
  ) +
  theme_classic() 

plot
```



```{r}
plot <- df %>% filter(response1_site == 'marina' | response2_site == 'marina') %>% 
  select(fieldsite, participants, fieldworker, response1_site, response1_gay, response1_euphemism,response1_diversity, response2_site, response2_gay,response2_euphemism,response2_diversity) %>% 
  mutate(response_gay = ifelse(response1_gay+response2_gay<=1, response1_gay+response2_gay,1),
         response_euphemism = ifelse(response1_euphemism+response2_euphemism<=1, response1_euphemism+response2_euphemism,1),
         response_diversity = ifelse(response1_diversity+response2_diversity<=1, response1_diversity+response2_diversity,1),
         response_gay_and_euphemism = response_gay + response_euphemism)%>% 
  ggplot(aes(x=fieldsite,y=response_diversity))+
           stat_summary(fun = "mean",
                        geom = "bar") +
  labs(
    title = "Proportion responses describing Marina with diversity",
    x = "Fieldsite",
    y = "Proportion diversity responses / total",
    color = "Species Type" # Changes the legend title
  )
  
```

```{r}
color_bar <- df.castro1 %>%
  filter(response_gay == 1 | response_euphemism == 1) %>% 
  ggplot(mapping = aes(x = fieldsite, y=response_euphemism))+
  stat_summary(fun = "mean",
               geom= "bar") +
  labs(
    title = "Proportion euphemism out of total gay responses for Castro",
    x = "Fieldsite",
    y = "Proportion euphemism responses / total gay responses",
    color = "Species Type" # Changes the legend title,
    ) + 
  theme_classic()

color_bar
```



